Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement Simulations with Adaptive Ray Tracing

### 2010-08-21 ms.tex
Cleared some ambiguities in the constant dt section.

If the timestep is too large, the ionization front will propagate too
slowly, but it evenutually approaches the correct radius at late times
(see \S\ref{sec:dt_dep}).  This does not prevent one from using a
large timestep, particularly if the system is not critically affected
by a slower I-front velocity.  One example is an expanding \ion{H}{2}
region in a power-law density gradient.  After a brief, initial R-type
phase, the I-front becomes D-type phase, where the ionization and
shock front progress jointly at the sound speed of the ionized region.
A moderately large (\textbf{show how large!}) timestep can accurately
follow its evolution.  However after the I-front passes a critical
radius \citep[show this!][]{Franco90}, the I-front detaches from the
shock front and accelerates.  The I-front velocities in these two
stages differ up to a factor of $\sim100$ (\textbf{check this!}).
Although the solution is accurate with a large timestep in the D-type
phase, the I-front may lag behind because of the constant timestep.
After a few recombination times, the numerical solution evenutally
approaches the analytical solution.  If such a simulation focuses on
the density core expansion and any small scale structures, such as
cometary structures and photo-dissociation regions, one can cautiously
sacrifice temporal accuracy at large scales for computational savings.

>>>>

If the timestep is too large, the ionization front will propagate too
slowly, but it evenutually approaches the correct radius at late times
(see \S\ref{sec:dt_dep}).  This does not prevent one from using a
large timestep, particularly if the system is not critically affected
by a slower I-front velocity.  One example is an expanding \ion{H}{2}
region in a power-law density gradient.  After a brief, initial R-type
phase, the I-front becomes D-type phase, where the ionization and
shock front progress jointly at the sound speed of the ionized region.
A moderately large (0.1 Myr) timestep can accurately follow its
evolution.  However after the I-front passes a critical radius
\citep{Franco90}, the I-front detaches from the shock front,
accelerates, and transitions back to an R-type front.  This can also
occur in champange flows when the ionization front passes a density
discontinuity.  The I-front velocities in these two stages differ up
to a factor of $\sim10$.  Although the solution is accurate with a
large timestep in the D-type phase, the I-front may lag behind because
of the constant timestep.  After a few recombination times, the
numerical solution evenutally approaches the analytical solution.  If
such a simulation focuses on the density core expansion and any small
scale structures, such as cometary structures and photo-dissociation
regions, one can cautiously sacrifice temporal accuracy at large
scales for computational savings.
